Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-29 paper.qmd
Ref to sec2 para:1

<!-- - Connection between NLDR and MDS-->
Historically, $k-D$ representations of $p-D$ data have been computed using multidimensional Scaling (MDS), which includes principal components analysis (PCA) as a special case.  The $k-D$ representation can be considered to be a layout of points in $k-D$ produced by an embedding procedure that maps the data from $p-D$. In MDS, the $k-D$ layout is constructed by minimizing a stress function that differences distances between points in $p-D$ with potential distances between points in $k-D$. Various formulations of the stress function result in non-metric scaling [@article62] and isomap [@article63]. Challenges in working with high-dimensional data, including visualization, are outlined in @Johnstone2009.

>>>>

<!-- - Connection between NLDR and MDS-->
Historically, $k-D$ representations of $p-D$ data have been computed using multidimensional Scaling (MDS) [@borg2005], which includes principal components analysis (PCA) as a special case.  The $k-D$ representation can be considered to be a layout of points in $k-D$ produced by an embedding procedure that maps the data from $p-D$. In MDS, the $k-D$ layout is constructed by minimizing a stress function that differences distances between points in $p-D$ with potential distances between points in $k-D$. Various formulations of the stress function result in non-metric scaling [@article62] and isomap [@article63]. Challenges in working with high-dimensional data, including visualization, are outlined in @johnstone2009.
